A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-10 paper/paper.tex
Removed a line
Corrected line-range grammar

\newcommand{\lineref}[1]{line~\ref{#1}}
\newcommand{\twolinesref}[2]{lines~\ref{#1} and~\ref{#2}}
\newcommand{\Lineref}[1]{Line~\ref{#1}}
\newcommand{\Twolinesref}[2]{Lines~\ref{#1} and~\ref{#2}}

@@

\Lineref{StoreIncumbent} stores the current mapping $M$ if it is large enough
to unseat the incumbent.  \Twolinesref{SetBestFutureToZero}{PruneSearch} prune
the search when a calculated upper bound ($\AlgVar{bestFuture}$) is not larger
than the incumbent.

The remainder of $\FuncSty{expand}$ performs the search.  A label-class
$\langle P, T \rangle$ is selected from $\AlgVar{future}$
(\lineref{SelectClass}) using some heuristic.  From this class, a pattern
vertex $v$ is selected using a heuristic (\lineref{SelectVertex}). We now
iterate over all possible vertices in $T$ (\twolinesref{WLoop}{ShrinkM}). A
vertex $w \in \V(H)$ is selected mapping $M$ is extended (\lineref{GrowM}). A
new set of label-classes, $\AlgVar{future'}$, is created (\lineref{NewFuture}).
Every label-class in $\AlgVar{future}$ can now be split
(\twolinesref{InnerLoop}{InnerLoopEnd}) into two new classes. The first of
these classes (\twolinesref{NewPWithEdge}{AddToFutureWithEdge}) contains
pattern vertices adjacent to $v$ and target vertices adjacent to $w$.  This is
added to $\AlgVar{future'}$ if both sets contain at least one vertex.  This is
then repeated symmetrically for non-adjacency
(\twolinesref{NewPWithoutEdge}{InnerLoopEnd}) using the compliments of the
graphs.  A recursive call is then made (\lineref{ExpandWithV}), on return from
which we remove the mapping $(v,w)$.  Having explored all possible mappings of
$v$ its target set we now consider what happens if $v$ is not matched
(\twolinesref{RemoveV}{ExpandWithoutV}). Note that removing $v$ from its label
class is equivalent in effect to assigning it the label $\bot$, which is never
taken by any vertex in $\V(H)$.

@@

? Describe CP-FC and clique encodings

>>>>

\newcommand{\lineref}[1]{line~\ref{#1}}
\newcommand{\linerangeref}[2]{lines~\ref{#1} to~\ref{#2}}
\newcommand{\Lineref}[1]{Line~\ref{#1}}
\newcommand{\Linerangeref}[2]{Lines~\ref{#1} to~\ref{#2}}

@@

\Lineref{StoreIncumbent} stores the current mapping $M$ if it is large enough
to unseat the incumbent.  \Linerangeref{SetBestFutureToZero}{PruneSearch} prune
the search when a calculated upper bound ($\AlgVar{bestFuture}$) is not larger
than the incumbent.

The remainder of $\FuncSty{expand}$ performs the search.  A label-class
$\langle P, T \rangle$ is selected from $\AlgVar{future}$
(\lineref{SelectClass}) using some heuristic.  From this class, a pattern
vertex $v$ is selected using a heuristic (\lineref{SelectVertex}). We now
iterate over all possible vertices in $T$ (\linerangeref{WLoop}{ShrinkM}). A
vertex $w \in \V(H)$ is selected mapping $M$ is extended (\lineref{GrowM}). A
new set of label-classes, $\AlgVar{future'}$, is created (\lineref{NewFuture}).
Every label-class in $\AlgVar{future}$ can now be split
(\linerangeref{InnerLoop}{InnerLoopEnd}) into two new classes. The first of
these classes (\linerangeref{NewPWithEdge}{AddToFutureWithEdge}) contains
pattern vertices adjacent to $v$ and target vertices adjacent to $w$.  This is
added to $\AlgVar{future'}$ if both sets contain at least one vertex.  This is
then repeated symmetrically for non-adjacency
(\linerangeref{NewPWithoutEdge}{InnerLoopEnd}) using the compliments of the
graphs.  A recursive call is then made (\lineref{ExpandWithV}), on return from
which we remove the mapping $(v,w)$.  Having explored all possible mappings of
$v$ its target set we now consider what happens if $v$ is not matched
(\linerangeref{RemoveV}{ExpandWithoutV}). Note that removing $v$ from its label
class is equivalent in effect to assigning it the label $\bot$, which is never
taken by any vertex in $\V(H)$.

@@
